### 2024-11-08 README.Rmd
get_similarities + code formatting

Common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). Includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, and reducing dimensionality.

@@

>>>>

embeddingplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). Includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, and reducing dimensionality.

@@

Functions for similarity and distance metrics are as simple as possible:

```{r}
vec1 <- c(1, 5, 2)
vec2 <- c(4, 2, 2)
vec3 <- c(1, -2, -13)

dot_prod(vec1, vec2)            # dot product
cos_sim(vec1, vec2)             # cosine similarity
euc_dist(vec1, vec2)            # Euclidean distance
anchored_sim(vec1, vec2, vec3)  # projection to an anchored vector
```
